Report

### 2020-11-13 report.Rmd
Update report

@@

library(drake)
library(tidyverse)
library(magrittr)
library(cowplot)
library(viridis)
library(kableExtra)
source("R/misc.R") # Define your custom code as a bunch of functions.
source_dir(get_mypath("R")) # Define your custom code as a bunch of functions.

@@

```{r}
loadd(log_bm_net_group)
```

```{r, fig.height = 12, fig.width = 12}
log_bm_net_group %>%
  ggplot(aes(x = bm_slope, y = linear_slope, color = log(bm))) +
  geom_point() +
  scale_color_viridis() +
  geom_errorbar(aes(xmin = bm_slope - bm_slope_strd_error,
      xmax = bm_slope + bm_slope_strd_error), alpha = .3) +
  geom_errorbar(aes(ymin = linear_slope - linear_slope_strd_error,
      ymax = linear_slope + linear_slope_strd_error), alpha = .3) +
  facet_wrap(~variable, scales = "free") +
  labs_log_bm_net_trends()
```

```{r, fig.height = 12, fig.width = 12}
log_bm_net_group %>%
  filter(!is.na(protocol_type)) %>%
  ggplot(aes(x = bm_slope, y = linear_slope, color = log(bm))) +
  geom_point() +
  scale_color_viridis() +
  geom_errorbar(aes(xmin = bm_slope - bm_slope_strd_error,
      xmax = bm_slope + bm_slope_strd_error), alpha = .3) +
  geom_errorbar(aes(ymin = linear_slope - linear_slope_strd_error,
      ymax = linear_slope + linear_slope_strd_error), alpha = .3) +
  facet_grid(variable~protocol_type, scales = "free") +
  labs_log_bm_net_trends()

log_bm_net_group %>%
  filter(variable == "connectance") %>%
  ggplot(aes(x = bm_slope, y = bm)) +
  geom_point()
  labs(x = "Biomass trends (log biomass per year)", y = "Biomass")
```

@@

```{r}
loadd(model_log_bm, model_log_bm_summary)
```

@@

unique(model_log_bm_summary$variable)
model_log_bm_table <- model_log_bm_summary %>%
  filter(model == "mod_bm_quad2") %>%
  filter(!variable %in% c("log_rich_std", "nbnode_std")) %>%
  mutate(
    reg_table = map(model_obj, broom::tidy),
    anova_table = map(anova, broom::tidy)
  )

@@

```{r, fig.height = 12, fig.width = 12}
pred_log_bm_quad2 <- model_log_bm_summary %>%
  filter(model == "mod_bm_quad2") %>%
  mutate(
    pred = map(model_obj, ~ggpredict(.x,
	terms = c("bm_slope", "bm [quart2]"))),
    pred_df = map(pred, as_tibble),
    plot = map(pred, ~plot(.x, add.data = FALSE)),
    plot_data = map(pred, ~plot(.x, add.data = TRUE)),
    #myplot = map2(pred, data, ~plot_final_model(ggpred = .x, rawdata = .y))
  )

@@

```{r}
myload(habitat_press, habitat_pressure,
  envir = environment(),
  dir = get_mypath("data"))
#habitat_press
```

```{r}
test <- log_bm_net_group %>%
  filter(variable == "connectance") %>%
  left_join(habitat_pressure, by = "station")
test %>%
  pivot_longer(
    cols = c(bm, width_river_mean, temperature_med, alt , RC1, RC2),
    names_to = "evt_var", values_to = "value") %>%
ggplot(aes(y = bm_slope, x = value)) +
geom_point() +
facet_wrap(~evt_var, scales = "free_x")
```

```{r}
library(sf)
myload(region_polygon, envir = environment(), dir = get_mypath("data"))
myload(station_analysis,
  envir = environment(),
  dir = "~/Documents/post-these/mnhn/fishcom/data")

@@

@@

```{r}
loadd(bm_net_group, log_bm_net_group, bm_vs_net_trends)
bm_vs_net_trends %>%
  ggplot(aes(x = reg_weight)) +
  geom_histogram() +
  facet_wrap(~variable)

bm_net_group %>%
  ggplot(aes(x = bm_slope, y = linear_slope, size = reg_weight, weight = reg_weight, color = log(bm))) +
  geom_point() +
  scale_color_viridis() +
  geom_vline(xintercept = 0, color = "red") +
  geom_smooth() +
  facet_wrap(~variable, scales = "free_y") +
  labs(x = "Biomass trend (g.m-1.y-1)", y = "Network trend (U.y-1)")

log_bm_net_group %>%
  ggplot(aes(x = bm_slope, y = linear_slope, size = reg_weight, weight = reg_weight, color = log(bm))) +
  geom_point() +
  scale_color_viridis() +
  geom_vline(xintercept = 0, color = "red") +
  geom_smooth() +
  facet_wrap(~variable, scales = "free_y") +
  labs(x = "Log Biomass trend (g.m-1.y-1)", y = "Network trend (U.y-1)")
```

@@

```{r}
loadd(bm_net_group)
loadd(log_bm_net_group)

bm_net_group %>%
  ggplot(aes(x = bm_slope, y = linear_slope, color = log(bm), size = reg_weight, weight = reg_weight)) +
  geom_point() +
  scale_color_viridis() +
  #geom_smooth(method = "lm") +
  facet_wrap(~variable, scales = "free") +
  labs(title = "Group as mean biomass")

bm_net_group %>%
  ggplot(aes(x = bm_slope, y = linear_slope, color = log(bm))) +
  geom_point() +
  scale_color_viridis() +
  geom_errorbar(aes(
      xmin = bm_slope - bm_slope_strd_error,
      xmax = bm_slope + bm_slope_strd_error),
    alpha = .2
    ) +
  geom_errorbar(aes(
      ymin = linear_slope - linear_slope_strd_error,
      ymax = linear_slope + linear_slope_strd_error),
    alpha = .2
    ) +
  facet_wrap(~variable, scales = "free") +
  labs(title = "Group as mean biomass")

bm_net_group %>%
  filter(!is.na(protocol_type)) %>%
  ggplot(aes(x = bm_slope, y = linear_slope, color = log(bm), size = reg_weight, weight = reg_weight)) +
  geom_point() +
  scale_color_viridis() +
  #geom_smooth(method = "lm") +
  facet_grid(variable~protocol_type, scales = "free") +
  labs(title = "Group as mean biomass")
```

@@

```{r}
pred_log_bm_quad <- model_log_bm_summary %>%
  filter(model == "mod_bm_quad") %>%
  mutate(
    pred = map(model_obj, ~ggpredict(.x,
	terms = c("bm_slope", "bm [quart2]"))),
    pred_df = map(pred, as_tibble),
    plot = map(pred, ~plot(.x, add.data = FALSE)),
    plot_data = map(pred, ~plot(.x, add.data = TRUE)),
    #myplot = map2(pred, data, ~plot_final_model(ggpred = .x, rawdata = .y))
  )

@@

```{r}
loadd(log_bm_net_group, model_log_bm_vif)

model_log_bm_vif %>%
  ggplot(aes(y= vif, x = term)) +
  geom_hline(yintercept = 10) +
  geom_bar(stat = "identity") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  facet_grid(model_type~variable, scales = "free")
```

@@

```{r}
loadd(model_log_bm_by_protocol_vif)

protocol_vec <- model_log_bm_by_protocol_vif$protocol_type %>% unique
p_vif_protocol <- map(protocol_vec, function (x) {
  model_log_bm_by_protocol_vif %>%
    filter(protocol_type == x) %>%
    ggplot(aes(y= vif, x = term)) +
    geom_hline(yintercept = 10) +
    geom_bar(stat = "identity") +
    theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
    labs(title = paste0("Protocol type: ", x)) +
    facet_grid(model_type~variable, scales = "free_y")
  })
p_vif_protocol[[1]]
p_vif_protocol[[2]]
```

```{r}
loadd(model_log_bm_by_protocol, model_log_bm_by_protocol_summary)
```

```{r, eval = FALSE}
complete_log_quad2 <- model_log_bm_by_protocol_summary %>%
  filter(model == "mod_bm_quad2", protocol_type == "complete") %>%
  mutate(
    reg_table = map(model_obj, broom::tidy),
    anova_table = map(anova, broom::tidy)
  )

@@

```{r, eval = FALSE}
filter(model_log_bm_by_protocol_summary, model == "mod_log_bm_inc")[["resume"]]
filter(model_log_bm_by_protocol_summary, model == "mod_log_bm_inc")[["anova"]]

filter(model_log_bm_by_protocol_summary, model == "mod_bm_quad")[["resume"]]
filter(model_log_bm_by_protocol_summary, model == "mod_log_bm_inc")[["anova"]]
```

@@

```{r}
pred_log_bm_quad2 <- model_log_bm_by_protocol_summary %>%
  filter(model == "mod_bm_quad2", protocol_type == "complete") %>%
  mutate(
    pred = map(model_obj, ~ggpredict(.x,
	terms = c("bm_slope", "bm [quart2]"))),
    pred_df = map(pred, as_tibble),
    plot = map(pred, ~plot(.x, add.data = FALSE)),
    plot_data = map(pred, ~plot(.x, add.data = TRUE)),
    #myplot = map2(pred, data, ~plot_final_model(ggpred = .x, rawdata = .y))
  )
model_log_bm_by_protocol %<>% filter(protocol_type == "complete")

@@

```{r}
pred_log_bm_quad <- model_log_bm_by_protocol_summary %>%
  filter(model == "mod_bm_quad", protocol_type == "complete") %>%
  mutate(
    pred = map(model_obj, ~ggpredict(.x,
	terms = c("bm_slope", "bm [quart2]"))),
    pred_df = map(pred, as_tibble),
    plot = map(pred, ~plot(.x, add.data = FALSE)),
    plot_data = map(pred, ~plot(.x, add.data = TRUE)),
    #myplot = map2(pred, data, ~plot_final_model(ggpred = .x, rawdata = .y))
  )
model_log_bm_by_protocol %<>% filter(protocol_type == "complete")

@@

```{r, eval = FALSE}
pred <- model_log_bm_by_protocol_summary %>%
  filter(model == "mod_log_bm_inc") %>%
  mutate(
    pred = map(model_obj, ~ggpredict(.x,
	terms = c("bm_slope", "log_bm [quart2]", "inc_f"))),
    pred_df = map(pred, as_tibble),
    plot = map(pred, ~plot(.x, add.data = FALSE)),
    plot_data = map(pred, ~plot(.x, add.data = TRUE)),
  )
plot_grid(plotlist = pred$plot, labels = pred$variable)
```

```{r, eval = FALSE}
pred <- model_log_bm_by_protocol_summary %>%
  filter(model == "mod_log_bm_inc") %>%
  mutate(
    pred = map(model_obj, ~ggpredict(.x,
	terms = c("bm_slope", "log_bm [quart2]", "inc_f"))),
    pred_df = map(pred, as_tibble),
    plot = map(pred, ~plot(.x, add.data = FALSE)),
    plot_data = map(pred, ~plot(.x, add.data = TRUE)),
  )
plot_grid(plotlist = pred$plot, labels = pred$variable)
```

@@

```{r}
cor_bm_net <- bm_net_group %>%
  select(bm_slope, variable, linear_slope, bm, width_river_mean) %>%
  pivot_wider(names_from = variable, values_from = linear_slope) 
corrplot::corrplot(cor(na.omit(cor_bm_net)), type = "upper")

>>>>

```{r, echo = FALSE}

knitr::opts_chunk$set(
  cache = FALSE,
  collapse = TRUE,
  comment = "#>",
  #fig.dim = c(7, 7),
  fig.fullwidth = TRUE,
  fig.show = "hold",
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  results = TRUE 
)
```

@@

library(drake)
library(tidyverse)
library(magrittr)
library(cowplot)
library(viridis)
library(kableExtra)
library(sf)
source("R/misc.R") # Define your custom code as a bunch of functions.
source("R/variable_shortcut.R")
source_dir(get_mypath("R")) # Define your custom code as a bunch of functions.

@@

```{r}
loadd(log_bm_net_group_median)
```

```{r, fig.height = 12, fig.width = 12}
log_bm_net_group_median %>%
  ggplot(aes(x = bm_slope, y = linear_slope, color = log(bm))) +
  geom_point() +
  scale_color_viridis() +
  geom_errorbar(aes(xmin = bm_slope - bm_slope_strd_error,
      xmax = bm_slope + bm_slope_strd_error), alpha = .3) +
  geom_errorbar(aes(ymin = linear_slope - linear_slope_strd_error,
      ymax = linear_slope + linear_slope_strd_error), alpha = .3) +
  facet_wrap(~variable, scales = "free") +
  labs_log_bm_net_trends()
```

```{r, fig.height = 12, fig.width = 12}
log_bm_net_group_median %>%
  filter(!is.na(protocol_type)) %>%
  ggplot(aes(x = bm_slope, y = linear_slope, color = log(bm))) +
  geom_point() +
  scale_color_viridis() +
  geom_errorbar(aes(xmin = bm_slope - bm_slope_strd_error,
      xmax = bm_slope + bm_slope_strd_error), alpha = .3) +
  geom_errorbar(aes(ymin = linear_slope - linear_slope_strd_error,
      ymax = linear_slope + linear_slope_strd_error), alpha = .3) +
  facet_grid(variable~protocol_type, scales = "free") +
  labs_log_bm_net_trends()

log_bm_net_group_median %>%
  filter(variable == "connectance") %>%
  ggplot(aes(x = bm_slope, y = bm)) +
  geom_point()
  labs(x = "Biomass trends (log biomass per year)", y = "Biomass")
```

@@

```{r}
loadd(model_log_bm, summary_log_bm)
```

@@

unique(summary_log_bm$variable)
model_log_bm_table <- summary_log_bm %>%
  filter(model == "mod_bm_quad2") %>%
  filter(!variable %in% c("log_rich_std", "nbnode_std")) %>%
  mutate(
    reg_table = map(model_obj, broom::tidy),
    anova_table = map(anova, broom::tidy)
  )

@@

```{r, fig.height = 12, fig.width = 12}
pred_log_bm_quad2 <- summary_log_bm %>%
  filter(model == "mod_bm_quad2") %>%
  mutate(
    pred = map(model_obj, ~ggpredict(.x,
	terms = c("bm_slope", "bm [quart2]"))),
    pred_df = map(pred, as_tibble),
    plot = map(pred, ~plot(.x, add.data = FALSE)),
    plot_data = map(pred, ~plot(.x, add.data = TRUE)),
    #myplot = map2(pred, data, ~plot_final_model(ggpred = .x, rawdata = .y))
  )

@@

```{r}
loadd(habitat_press, habitat_pressure)
#habitat_press
```

```{r}
test <- log_bm_net_group_median %>%
  filter(variable == "connectance") %>%
  left_join(habitat_pressure, by = "station")
test %>%
  pivot_longer(
    cols = c(bm, width_river_mean, temperature_med, alt , RC1, RC2),
    names_to = "evt_var", values_to = "value") %>%
ggplot(aes(y = bm_slope, x = value)) +
geom_point() +
facet_wrap(~evt_var, scales = "free_x")
```

```{r}
loadd(region_polygon, station_analysis)

@@

```{r}
log_bm_net_group_median %>%
  filter(variable == "rich_std", bm_slope < 0) %>%
  left_join(habitat_pressure, by = "station") %>%
  pivot_longer(cols = c(bm, width_river_mean, temperature_med, alt , RC1, RC2),
    names_to = "evt_var", values_to = "value") %>%
ggplot(aes(y = linear_slope, x = value)) +
geom_point() +
facet_wrap(~evt_var, scales = "free_x")
```

```{r}
loadd(richness_group)
rich_std_f3y <- richness_group %>% 
  filter(rich_var == "rich_std", summary_type == "first_3_year", group_type ==
    "median") %>%
  select(station, rich)

log_bm_net_group_median %>%
  filter(variable == "rich_std", bm_slope < 0) %>%
  left_join(rich_std_f3y, by = "station") %>%
  ggplot(aes(y = linear_slope, x = rich)) +
  geom_point()
```

@@

```{r}
loadd(bm_net_group_median, log_bm_net_group_median, bm_vs_net_trends)
bm_vs_net_trends %>%
  ggplot(aes(x = reg_weight)) +
  geom_histogram() +
  facet_wrap(~variable)

bm_net_group_median %>%
  ggplot(aes(x = bm_slope, y = linear_slope, size = reg_weight, weight = reg_weight, color = log(bm))) +
  geom_point() +
  scale_color_viridis() +
  geom_vline(xintercept = 0, color = "red") +
  geom_smooth() +
  facet_wrap(~variable, scales = "free_y") +
  labs(x = "Biomass trend (g.m-1.y-1)", y = "Network trend (U.y-1)")

log_bm_net_group_median %>%
  ggplot(aes(x = bm_slope, y = linear_slope, size = reg_weight, weight = reg_weight, color = log(bm))) +
  geom_point() +
  scale_color_viridis() +
  geom_vline(xintercept = 0, color = "red") +
  geom_smooth() +
  facet_wrap(~variable, scales = "free_y") +
  labs(x = "Log Biomass trend (g.m-1.y-1)", y = "Network trend (U.y-1)")
```

@@

```{r}
loadd(bm_net_group_median)
loadd(log_bm_net_group_median)

bm_net_group_median %>%
  ggplot(aes(x = bm_slope, y = linear_slope, color = log(bm), size = reg_weight, weight = reg_weight)) +
  geom_point() +
  scale_color_viridis() +
  #geom_smooth(method = "lm") +
  facet_wrap(~variable, scales = "free") +
  labs(title = "Group as mean biomass")

bm_net_group_median %>%
  ggplot(aes(x = bm_slope, y = linear_slope, color = log(bm))) +
  geom_point() +
  scale_color_viridis() +
  geom_errorbar(aes(
      xmin = bm_slope - bm_slope_strd_error,
      xmax = bm_slope + bm_slope_strd_error),
    alpha = .2
    ) +
  geom_errorbar(aes(
      ymin = linear_slope - linear_slope_strd_error,
      ymax = linear_slope + linear_slope_strd_error),
    alpha = .2
    ) +
  facet_wrap(~variable, scales = "free") +
  labs(title = "Group as mean biomass")

bm_net_group_median %>%
  filter(!is.na(protocol_type)) %>%
  ggplot(aes(x = bm_slope, y = linear_slope, color = log(bm), size = reg_weight, weight = reg_weight)) +
  geom_point() +
  scale_color_viridis() +
  #geom_smooth(method = "lm") +
  facet_grid(variable~protocol_type, scales = "free") +
  labs(title = "Group as mean biomass")
```

@@

```{r}
pred_log_bm_quad <- summary_log_bm %>%
  filter(model == "mod_bm_quad") %>%
  mutate(
    pred = map(model_obj, ~ggpredict(.x,
	terms = c("bm_slope", "bm [quart2]"))),
    pred_df = map(pred, as_tibble),
    plot = map(pred, ~plot(.x, add.data = FALSE)),
    plot_data = map(pred, ~plot(.x, add.data = TRUE)),
    #myplot = map2(pred, data, ~plot_final_model(ggpred = .x, rawdata = .y))
  )

@@

```{r}
loadd(log_bm_net_group_median, vif_log_bm)

vif_log_bm %>%
  ggplot(aes(y= vif, x = term)) +
  geom_hline(yintercept = 10) +
  geom_bar(stat = "identity") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  facet_grid(model_type~variable, scales = "free")
```

@@

```{r}
loadd(vif_log_bm_by_protocol)

protocol_vec <- vif_log_bm_by_protocol$protocol_type %>% unique
p_vif_protocol <- map(protocol_vec, function (x) {
  vif_log_bm_by_protocol %>%
    filter(protocol_type == x) %>%
    ggplot(aes(y= vif, x = term)) +
    geom_hline(yintercept = 10) +
    geom_bar(stat = "identity") +
    theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
    labs(title = paste0("Protocol type: ", x)) +
    facet_grid(model_type~variable, scales = "free_y")
  })
p_vif_protocol[[1]]
p_vif_protocol[[2]]
```

```{r}
loadd(model_log_bm_by_protocol, summary_log_bm_by_protocol)
```

```{r, eval = FALSE}
complete_log_quad2 <- summary_log_bm_by_protocol %>%
  filter(model == "mod_bm_quad2", protocol_type == "complete") %>%
  mutate(
    reg_table = map(model_obj, broom::tidy),
    anova_table = map(anova, broom::tidy)
  )

@@

```{r, eval = FALSE}
filter(summary_log_bm_by_protocol, model == "mod_log_bm_inc")[["resume"]]
filter(summary_log_bm_by_protocol, model == "mod_log_bm_inc")[["anova"]]

filter(summary_log_bm_by_protocol, model == "mod_bm_quad")[["resume"]]
filter(summary_log_bm_by_protocol, model == "mod_log_bm_inc")[["anova"]]
```

@@

```{r}
pred_log_bm_quad2 <- summary_log_bm_by_protocol %>%
  filter(model == "mod_bm_quad2", protocol_type == "complete") %>%
  mutate(
    pred = map(model_obj, ~ggpredict(.x,
	terms = c("bm_slope", "bm [quart2]"))),
    pred_df = map(pred, as_tibble),
    plot = map(pred, ~plot(.x, add.data = FALSE)),
    plot_data = map(pred, ~plot(.x, add.data = TRUE)),
    #myplot = map2(pred, data, ~plot_final_model(ggpred = .x, rawdata = .y))
  )
model_log_bm_by_protocol %<>% filter(protocol_type == "complete")

@@

```{r}
pred_log_bm_quad <- summary_log_bm_by_protocol %>%
  filter(model == "mod_bm_quad", protocol_type == "complete") %>%
  mutate(
    pred = map(model_obj, ~ggpredict(.x,
	terms = c("bm_slope", "bm [quart2]"))),
    pred_df = map(pred, as_tibble),
    plot = map(pred, ~plot(.x, add.data = FALSE)),
    plot_data = map(pred, ~plot(.x, add.data = TRUE)),
    #myplot = map2(pred, data, ~plot_final_model(ggpred = .x, rawdata = .y))
  )
model_log_bm_by_protocol %<>% filter(protocol_type == "complete")

@@

```{r, eval = FALSE}
pred <- summary_log_bm_by_protocol %>%
  filter(model == "mod_log_bm_inc") %>%
  mutate(
    pred = map(model_obj, ~ggpredict(.x,
	terms = c("bm_slope", "log_bm [quart2]", "inc_f"))),
    pred_df = map(pred, as_tibble),
    plot = map(pred, ~plot(.x, add.data = FALSE)),
    plot_data = map(pred, ~plot(.x, add.data = TRUE)),
  )
plot_grid(plotlist = pred$plot, labels = pred$variable)
```

```{r, eval = FALSE}
pred <- summary_log_bm_by_protocol %>%
  filter(model == "mod_log_bm_inc") %>%
  mutate(
    pred = map(model_obj, ~ggpredict(.x,
	terms = c("bm_slope", "log_bm [quart2]", "inc_f"))),
    pred_df = map(pred, as_tibble),
    plot = map(pred, ~plot(.x, add.data = FALSE)),
    plot_data = map(pred, ~plot(.x, add.data = TRUE)),
  )
plot_grid(plotlist = pred$plot, labels = pred$variable)
```

@@

```{r}
cor_bm_net <- bm_net_group_median %>%
  select(bm_slope, variable, linear_slope, bm, width_river_mean) %>%
  pivot_wider(names_from = variable, values_from = linear_slope) 
corrplot::corrplot(cor(na.omit(cor_bm_net)), type = "upper")
